---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
The data relevant for this submission is in a standard csv file.
```{r}
data <- read.csv("activity.csv")
```
The column names in  the data set are: `r colnames(data)`.

## What is mean total number of steps taken per day?
```{r}
library(dplyr)
totalperday <- group_by(data,date)
totalperday <- summarize(totalperday,steps=sum(steps))
hist(totalperday$steps)
totalmean  <- mean(totalperday$steps, na.rm=TRUE)
totalmedian <- median(totalperday$steps, na.rm=TRUE)
print(totalmean)
print(totalmedian)
```

## What is the average daily activity pattern?
```{r}
library(dplyr)
dailypattern <- group_by(data,interval)
dailypattern <- summarize(dailypattern,steps=mean(steps,na.rm=TRUE))
max <- max(dailypattern$steps)
limit <- max+max(dailypattern$steps)/10
plot(dailypattern$interval/100,dailypattern$steps,type="l",ylim=c(0,limit))
```

The average maximum number of steps done in a 5 minute intervall is `r round(max,2)`.
```{r, echo=FALSE}
subset <- dailypattern[dailypattern$steps==max,]
hour <- floor(subset$interval/100)
min <- subset$interval - hour*100
```
The average maximum number of steps are done between `r hour`:`r min-5` and `r hour`:`r min` 

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
