---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
The data relevant for this submission is in a standard csv file.
```{r}
data <- read.csv("activity.csv")
```
The column names in  the data set are: `r colnames(data)`.

## What is mean total number of steps taken per day?
```{r}
library(dplyr)
totalperday <- group_by(data,date)
totalperday <- summarize(totalperday,steps=sum(steps))
hist(totalperday$steps)
totalmean  <- mean(totalperday$steps, na.rm=TRUE)
totalmedian <- median(totalperday$steps, na.rm=TRUE)
print(totalmean)
print(totalmedian)
```

## What is the average daily activity pattern?
```{r}
library(dplyr)
dailypattern <- group_by(data,interval)
dailypattern <- summarize(dailypattern,steps=mean(steps,na.rm=TRUE))
max <- max(dailypattern$steps)
limit <- max+max(dailypattern$steps)/10
plot(dailypattern$interval/100,dailypattern$steps,type="l",ylim=c(0,limit))
```

The average maximum number of steps done in a 5 minute intervall is `r round(max,2)`.
```{r, echo=FALSE}
subset <- dailypattern[dailypattern$steps==max,]
hour <- floor(subset$interval/100)
min <- subset$interval - hour*100
```
The average maximum number of steps are done between `r hour`:`r min-5` and `r hour`:`r min` 

## Imputing missing values
First lets count the number of NA available in the data set.
```{r}
nadata <- is.na(data$steps)
sum(nadata)
```
The number of NAs availbale in the dataset are `r sum(nadata)`.

The proposed strategy in the Assessment is to fill in mean/median in the NAs.
I'll replace the NA with the mean of the corrisponding 5-minute intervall.
```{r}
grouped <- group_by(data,date)
meanperday <- summarize(grouped,meanperday=mean(steps,na.rm=TRUE))
temp <- data
for(i in meanperday$date){
       for(j in temp[temp$date==i,3]){
               temp[temp$date==i & temp$interval==j,1] <- meanperday[meanperday$date==i,1]
       }
}
```
Here the histogramm of total number of steps per day for the data without NA's:
```{r}
resultset <- group_by(temp,date)
resultset <- summarize(resultset,steps=sum(steps))
hist(resultset$steps)
```

The mean of steps per day now is `r mean(resultset$steps)` and the median of steps per day now is `r median(resultset$steps)`


## Are there differences in activity patterns between weekdays and weekends?
